### 2018-11-28 Sections/routing_strategies.tex
Added zuens updated SotA

Let us consider a simple example scenario. Imagine we begin with an ordinary network graph, with edges weighted by costs and attributes. For generality, we will additionally assume the available network resources are very dynamic and unpredictable. The costs associated with links are at the whim of market forces we do not understand (do we ever?). And, for the sake of example, and to make matters worse, the links have been very unreliable lately, and are routinely dropping in and out -- `blackouts'. This effectively rules out \textit{a priori} route optimisation, requiring something dynamic.

>>>>

Let us consider a simple example scenario. Imagine we begin with an ordinary network graph, with edges weighted by costs and attributes. For generality, we will additionally assume the available network resources are very dynamic and unpredicTab.~\ref The costs associated with links are at the whim of market forces we do not understand (do we ever?). And, for the sake of example, and to make matters worse, the links have been very unreliable lately, and are routinely dropping in and out -- `blackouts'. This effectively rules out \textit{a priori} route optimisation, requiring something dynamic.
